---
title: "Modeling Kobe"
author: "Daniel Byrne"
date: "April 12, 2019"
output:
  word_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(mosaic)
library(aod)
library(kableExtra)
layout(matrix(c(1,2,3,4),2,2))
```


```{r}
# read data
kobe = read.csv("./project2Data.csv")

# set factors
kobe$action_type = factor(kobe$action_type)
kobe$shot_type = factor(kobe$shot_type)
kobe$combined_shot_type = factor(kobe$combined_shot_type)
kobe$shot_zone_area = factor(kobe$shot_zone_area)
kobe$shot_zone_basic = factor(kobe$shot_zone_basic)
kobe$shot_zone_range = factor(kobe$shot_zone_range)
kobe$season = factor(kobe$season)
kobe$playoffs = factor(kobe$playoffs)
kobe$shot_made_flag = factor(kobe$shot_made_flag)
kobe$period = factor(kobe$period)
kobe$season = factor(kobe$season)
kobe$playoffs = factor(kobe$playoffs)

```

## Introduction

Kobe Bryant marked his retirement from basketball by scoring 60 points in his final game as a member of the Los Angeles Laker team on Wednesday, April 12, 2016. Starting to play professional basketball at the age of 17, Kobe earned the sport's highest accolades throughout his long career.  Using 20 years of data on Kobe's shots made and shots missed, we explore potential models that attempt to predict whether or not his shot went in.  This type of model could be used in building a simulation or video game in which a model can be used to predict whether or not a shot went in. 

## Data

The original data set contains the location and circumstances of every shot attempted by Bryant during his 20-year career. Your task is to predict whether the basket went in (shot_made_flag = 1) or missed (shot_made_flag = 0).  The data for estimation is in project2Data.xlsx.

## Questions

### The odds of Kobe making a shot decrease with respect to the distance he is from the hoop*

We explored several models trying to establish the odds Kobe's shot would fall in.  We summarized that the odds of the shot being good would decreae relatively lineraly as a function of the distance from the basket. 

The dataset contained several datpoints related to distance which we explored individually and in concert with other variables.  Two predictors, y_loc and shot_distance were highly colinear, and often were interchangeable in a model.  Most often however they interfered with each other when used together in the same model.

```{r}
predictors = kobe %>% dplyr::select(loc_y,shot_distance)
cor(predictors)
```

An analysis of the correlation matrix between the two predictors yielded a colineraity of about .8.

Alogistic regressionmodel consisting of the predictors shot_distance, combined_shot_type, and shot_type appeared to yield the most signifigant results. 

```{r}
shotdistance = glm(shot_made_flag ~ shot_distance + combined_shot_type + shot_type, data=kobe,family="binomial")
summary(shotdistance)

## CIs using standard errors
confint.default(shotdistance)
```

From the results in the table above, shot_distance, combined_shot_type, and shot_type all appear to be statistically signifigant.

```{r}
cstwald = wald.test(b = coef(shotdistance), Sigma = vcov(shotdistance), Terms = 3:7)
cstwald
```

The chi-squared test statistic of `cstwald$result$chi2["chi2"]`, with `cstwald$result$chi2["df"]` degrees of freedom is associated with a p-value << 0 indicates that the overall effect of combined_shot_type is statistically significant.


```{r}
wald.test(b = coef(shotdistance), Sigma = vcov(shotdistance), Terms = 8)
``` 

Furthermore the chi-squared test statistic of 12.6, with 1 degree of freedom and a p-value .0038 indicates that the overall effect of shot_type is statistically significant as well.


```{r, warning=FALSE}
# calculate odds ratios
oddsratios = exp(cbind(OR = coef(shotdistance), confint(shotdistance)))
kable(oddsratios, format = "pandoc")
```

For a one unit increase in shot_distance, the odds of Kobe making his shot decreases by ~2%.


```{r}
predictors = kobe %>% dplyr::select(shot_distance)
cor(predictors)
chisq.test(predictors)
```

### The probability of Kobe making a shot decreases linearly with respect to the distance he is from the hoop.

```{r}
 chisq()
```


### The relationship between the distance Kobe is from the basket and the odds of him making the shot is different if they are in the playoffs.