---
title: "Modeling Kobe"
author: "Daniel Byrne"
date: "April 12, 2019"
output:
  word_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(mosaic)
library(aod)
library(kableExtra)
layout(matrix(c(1,2,3,4),2,2))
```


```{r}
# read data
kobe = read.csv("./project2Data.csv")

# set factors
kobe$action_type = factor(kobe$action_type)
kobe$shot_type = factor(kobe$shot_type)
kobe$combined_shot_type = factor(kobe$combined_shot_type)
kobe$shot_zone_area = factor(kobe$shot_zone_area)
kobe$shot_zone_basic = factor(kobe$shot_zone_basic)
kobe$shot_zone_range = factor(kobe$shot_zone_range)
kobe$season = factor(kobe$season)
kobe$playoffs = factor(kobe$playoffs)
kobe$shot_made_flag = factor(kobe$shot_made_flag)
kobe$period = factor(kobe$period)
kobe$season = factor(kobe$season)
kobe$playoffs = factor(kobe$playoffs)
```

## Abstract

Sports data modeling has been a staple of video game development for many years.
The major leagues leagues NBA, NFL, NHL have all partnered with various software development
companies to produce ever more realistic video games depicting the leagues's top stars
acting and more importantly scoring as they do in real life.  With the $20 billion
video game industry fueled by the now growing e-sports segment. Ever more realistic models
are needed for developers to build the characters in their games.  We explore
a common dataset of Kobe Bryant's depicting the shots he made and missed over his
20 year career and try to build a model that would predict with a high degree of probability
the likelihood of his making or missing a shot.  We show that our final model is moderately successful
in predicting a shot.  We speculate that additional data points commonly captured in sport statistics
such as whether or not the shot was contested could add specificity to the model.  Also 

## Introduction

Kobe Bryant marked his retirement from basketball by scoring 60 points in his final game as a member of the Los Angeles Lakers team on Wednesday, April 12, 2016. Starting to play professional basketball at the age of 17, Kobe earned the sport's highest accolades throughout his long career.  Using 20 years of data on Kobe's shots made and shots missed, we explore potential models that attempt to predict whether or not his shot went in.  This type of model could be used in building a simulation or video game in which a model can be used to predict whether or not a shot went in. 
